### 2020-10-04 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
Reference to the new grant

\title{Computationally Efficient Approach for Solving Lexicographic Multicriteria Optimization Problems\thanks{This research was supported by the Russian Science Foundation, project No 16-11-10150. %``Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance''.
}
}

>>>>

\title{Computationally Efficient Approach for Solving Lexicographic Multicriteria Optimization Problems\thanks{The work was supported by the Ministry of Science and Higher Education of the Russian Federation, agreement No 13.1902.21.0026. %``Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance''.
}
}
